Lesson 3
========================================================

***

### What to Do First?
Notes: Read data

***

### Pseudo-Facebook User Data
Notes: fb seudo user data

```{r Pseudo-Facebook User Data}
getwd()
setwd('/home/williamn/Repository/dataAnalysis/udacity/data\ analysis\ R')
list.files()
pf<- read.csv('pseudo_facebook.tsv', sep = '\t')
```

***

### Histogram of Users' Birthdays
Notes: histogram of the users' birthdays

```{r Histogram of Users\' Birthdays}
# install.packages('ggplot2')
library(ggplot2)
library(ggthemes)

qplot(x = dob_day, data = pf) + 
    scale_x_discrete(breaks = 1:31) +
    theme_economist() +
    scale_colour_economist() +
    ggtitle("Fb users' birthdays")
```

***

#### What are some things that you notice about this histogram?
Response: Day one has the highest birthdays in a month

***

### Moira's Investigation
Notes: She wanted to know whether the perceived audience matches up the reality

***

### Estimating Your Audience Size
Notes: Audience on fb

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response: My last profile picture

#### How many of your friends do you think saw that post?
Response: 40

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response: 10

***

### Perceived Audience Size
Notes: 10

***
### Faceting
Notes:

```{r Faceting}
qplot(x = dob_day, data = pf) + 
    scale_x_discrete(breaks = 1:31) +
    facet_wrap(~dob_month, ncol = 3) +
    theme_economist() +
    scale_colour_economist() +
    ggtitle("Fb users' birthdays")
```

#### Let’s take another look at our plot. What stands out to you here?
Response: January 1st has the highest rate of birthdays of the year

***

### Be Skeptical - Outliers and Anomalies
Notes: January 1st

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira’s outlier?
Response: Bad data about extreme cases

***

### Friend Count
Notes: Number of friends

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
names(pf)
qplot(x = friend_count, data = pf)
```

#### How is this plot similar to Moira's first plot?
Response: The first bar is as big as Moira's first plot

***

### Limiting the Axes
Notes: When you want to focus on a significant range

```{r Limiting the Axes}
qplot(x = friend_count, data = pf, xlim = c(0, 1000))

qplot(x = friend_count, data = pf) +
    scale_x_continuous(limits = c(0, 1000))
```

### Exploring with Bin Width
Notes: Managing bin width allows to get a bether insight of the data

***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) +
    facet_wrap(~gender)
```

***

### Omitting NA Values
Notes: NA ~ Not applicable

```{r Omitting NA Values}
qplot(x = friend_count, data = subset(pf, !is.na(gender)), 
      xlim = c(0, 1000), xlab = seq(0, 1000, 50), binwidth = 25) +
    facet_wrap(~gender)
```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
table(pf$gender)
by(pf$friend_count, pf$gender, summary)
```

#### Who on average has more friends: men or women?
Response: women

#### What's the difference between the median friend count for women and men?
Response: 22

#### Why would the median be a better measure than the mean?
Response: because it represent better the average of friends than the mean

***

### Tenure
Notes: The number of days that somenone has been using fb

```{r Tenure}
qplot(x = tenure, data = pf, binwidth = 30, 
      color = I('black'), fill = I('#099DD9'))
```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
qplot(x = tenure/365, data = pf, binwidth = 0.25, 
      color = I('black'), fill = I('#F79420')) +
    scale_x_continuous(limits = c(0, 7), breaks = seq(1, 7, 1))
```

***

### Labeling Plots
Notes: Give us a better description of the plot

```{r Labeling Plots}
qplot(x = tenure/365, data = pf, 
      xlab = 'Number of years using Facebook', 
      ylab = 'Number of users in sample', 
      color = I('black'), fill = I('#F79420')) +
    scale_x_continuous(limits = c(0, 7), breaks = seq(1, 7, 1))
```

***

### User Ages
Notes:

```{r User Ages}
summary(pf$age)

qplot(x = age, data = pf, binwidth = 1, 
      xlab = 'Age of users', 
      ylab = 'Number of users in sample', 
      color = I('black'), fill = I('#099DD9')) +
    scale_x_continuous(limits = c(0, 113), breaks = seq(0, 113, 5))
```

#### What do you notice?
Response: Most of the users are between 15 to 30 years old

***

### The Spread of Memes
Notes: The frecuency of appearance of memes

***

### Lada's Money Bag Meme
Notes: october 2010

***

### Transforming Data
Notes: If the data doesn't have a normal distribution
```{r Transforming Data}
# install.packages('gridExtra')
library('gridExtra')

# Defining individual plots
summary(pf$friend_count)

p1<- qplot(x = friend_count, data = pf)
p2<- p1 + scale_x_log10()
p3<- p1 + scale_x_sqrt()

# Another way
p1<- qplot(x = friend_count, data = pf)
p2<- qplot(x = log10(friend_count + 1), data = pf)
p3<- qplot(x = sqrt(friend_count), data = pf)

# Alternate solution
p1<- ggplot(aes(x = friend_count), data = pf) + 
    geom_histogram()
p2<- p1 + scale_x_log10()
p3<- p1 + scale_x_sqrt()

# arrange plots in grid
grid.arrange(p1, p2, p3, ncol = 1)
```


***

### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}
ggplot(aes(x = friend_count), data = pf) + 
    geom_histogram() +
    scale_x_log10()
```

***


### Frequency Polygons

```{r Frequency Polygons}
qplot(x = friend_count, y = ..count../sum(..count..), 
      data = subset(pf, !is.na(gender)), 
      xlab = 'Friend count', 
      ylab = 'Proportion of users with that friend count',
      geom = 'freqpoly', color = gender) + 
    scale_x_continuous(lim = c(500, 1000), breaks = seq(500, 1000, 50))
```

***

### Likes on the Web
Notes: who has more likes males or females?

```{r Likes on the Web}
summary(pf$www_likes)

qplot(x = www_likes, 
      data = subset(pf, !is.na(gender)), 
      xlab = 'www_likes', 
      ylab = 'Number of users who like',
      geom = 'freqpoly', color = gender) + 
    scale_x_log10()

# Statistics about likes by gender
tail(pf)

# What's the www_like count for males?
by(pf$www_likes, pf$gender, summary)
maleLikes<- pf[pf$gender=='male',]
maleTotalLikes<- sum(maleLikes$www_likes, na.rm = TRUE)

# Alternate solution
by(pf$www_likes, pf$gender, sum)
```
#### What's the www_like count for males?
Response: 1430175

#### Which gender has more www_likes?
Response: females

***

### Box Plots
Notes: Summary information about the data in just one box

```{r Box Plots}
qplot(x = gender, y = friend_count, data = subset(pf, !is.na(gender)), 
      geom = 'boxplot')
```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}
# The data outside the range is ignored
qplot(x = gender, y = friend_count, data = subset(pf, !is.na(gender)), 
      geom = 'boxplot') + 
    scale_y_continuous(lim = c(0, 1000))

# Alternate code: coord_cartesian sets the viewing area of the data
qplot(x = gender, y = friend_count, data = subset(pf, !is.na(gender)), 
      geom = 'boxplot') + 
    coord_cartesian(ylim = c(0, 1000))
```

***

### Box Plots, Quartiles, and Friendships
Notes: 

```{r Box Plots, Quartiles, and Friendships}
qplot(x = gender, y = friend_count, data = subset(pf, !is.na(gender)), 
      geom = 'boxplot') + 
    coord_cartesian(ylim = c(0, 250))

by(pf$friend_count, pf$gender, summary)
```

#### On average, who initiated more friendships in our sample: men or women?
Response: women
#### Write about some ways that you can verify your answer.
Response: According to the box plot the median for females is higher than males.

```{r Friend Requests by Gender}
qplot(x = gender, y = friendships_initiated, data = subset(pf, !is.na(gender)), 
      geom = 'boxplot') + 
    coord_cartesian(ylim = c(0, 150))

by(pf$friendships_initiated, pf$gender, summary)
```

***

### Getting Logical
Notes: If we want to know whether someone has ever used a specific feature instead of the number of times that has used it.

```{r Getting Logical}
summary(pf$mobile_likes)

summary(pf$mobile_likes > 0)

pf$mobile_check_in<- NA
pf$mobile_check_in<- ifelse(pf$mobile_likes > 0, 1, 0)
pf$mobile_check_in<- factor(pf$mobile_check_in)
summary(pf$mobile_check_in)

percentage<- 63947/99003

# Using code
sum(pf$mobile_check_in == 1)/length(pf$mobile_check_in)
```

Response:

***

### Analyzing One Variable
Reflection: I've learned a lot

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!